Appendix 1: Preregistered analysis with simulated data

### 2025-04-29 preregistration.Rmd
Preregistration
PsychArchives request

Having a donor self-identity is considered a key motivational factor for sustained blood donation behavior [@calleroRoleidentitySalience1985,@fergusonTypologyBloodDonor2020]. Within Identity Theory, when a new donor first gives blood they develop a role-identity (I am a blood donor). As a novice donor continues to donate, this role-identity is validated, and thus blood donation becomes part of a donor’s self-identity (Being a blood donor is an important part of who I am; [@grubeRoleIdentityOrganizational2000,@masserPredictingBloodDonation2009]. However, despite the link between donor self-identity and donor retention, there are currently no interventions which can foster a sense of identity in donors that do not rely exclusively on repeat donation behavior. 
Psychological ownership (this is mine) is the sense of ownership experienced over both material (e.g., blood collection agency) and abstract immaterial (e.g., blood donation behavior) possessions [@pierceTheoryPsychologicalOwnership2001]. The ownership volunteers experience over a non-profit organisation has been linked to sustained volunteering behavior [@ainsworthFeelingsOwnershipVolunteering2020]. Further, psychological ownership is theoretically associated with identity as it has been proposed that through possession identity is established and maintained [@dittmarSocialPsychologyMaterial1992, @pierceTheoryPsychologicalOwnership2001]. 
In an Australian donor context, we have provided initial support for the idea that psychological ownership experienced towards a blood collection agency both increases with past donation experience and is positively associated with blood donor self-identity [@edwardsPsychologicalOwnershipIdentity2023]. Further, in a series of semi-structured interviews we have shown that Australian blood donors primarily expressed ownership over the blood donation process (role behaviour), not the blood collection agency (organisation). As such, interventions that enhance the amount of psychological ownership donors experience over their donation have the potential to impact donor retention. 
In this study we try to repeat results from Edwards et al., 2023 in Finland by collecting similar questionnaire data from donors of Finnish Red Cross Blood Service (FRCBS) and modeling the questionnaire data with a structural equation model. We include pre-registered R analysis code for direct repetition of Edwards et al., 2023 in Appendix 1.

@@

\includepdf[pages={-}]{preregistration_code.pdf}

>>>>

Having a donor self-identity is considered a key motivational factor for sustained blood donation behavior [@calleroRoleidentitySalience1985,@fergusonTypologyBloodDonor2020]. Within Identity Theory, when a new donor first gives blood they develop a role-identity (I am a blood donor). As a novice donor continues to donate, this role-identity is validated, and thus blood donation becomes part of a donor’s self-identity (Being a blood donor is an important part of who I am; [@grubeRoleIdentityOrganizational2000,@masserPredictingBloodDonation2009]. However, despite the link between donor self-identity and donor retention, there are currently no interventions which can foster a sense of identity in donors that do not rely exclusively on repeat donation behavior. 
Psychological ownership (this is mine) is the sense of ownership experienced over both material (e.g., blood collection agency) and abstract immaterial (e.g., blood donation behavior) possessions [@pierceTheoryPsychologicalOwnership2001]. The ownership volunteers experience over a non-profit organisation has been linked to sustained volunteering behavior [@ainsworthFeelingsOwnershipVolunteering2020]. Further, psychological ownership is theoretically associated with identity as it has been proposed that through possession identity is established and maintained [@dittmarSocialPsychologyMaterial1992, @pierceTheoryPsychologicalOwnership2001]. 
In an Australian donor context, we have provided initial support for the idea that psychological ownership experienced towards a blood collection agency both increases with past donation experience and is positively associated with blood donor self-identity [@edwardsPsychologicalOwnershipIdentity2023]. Further, in a series of semi-structured interviews we have shown that Australian blood donors primarily expressed ownership over the blood donation process (role behaviour), not the blood collection agency (organisation). As such, interventions that enhance the amount of psychological ownership donors experience over their donation have the potential to impact donor retention. 
In this study we try to repeat results from Edwards et al., 2023 in Finland by collecting similar questionnaire data from donors of Finnish Red Cross Blood Service (FRCBS) and modeling the questionnaire data with a structural equation model. We include pre-registered R analysis code for direct repetition of Edwards et al., 2023 in Appendix 1 (created in https://github.com/FRCBS/bd_psychological_ownership_prereg.git ).

@@

See Appendix 1 for preregistered analysis code in R with simulated data.
